### 2021-04-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

\section{Implementation}
We have implemented a prototype of \ctool{}. It takes an input of ELF binary as well as the source code of the corresponding problem. The front-end of \ctool{} is implemented in Python. It can generate random inputs and test the program with those inputs many times.  The address record part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input. The main component uses \textsf{libelfin}, an open source library to parse ELF binaries and read DWARF debug information. The current implementation can support both 64-bits and 32-bits ELF binary in Linux. \ctool{} will be open-sourced.

@@

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Leaked Functions}} & \multicolumn{2}{c}{\textbf{Max. Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  64 Bytes & 1 Byte  & 64 Bytes & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Unsafe Password Checker& 4096& 12.0& 1&0&0.04&  0& 18 & 104 KB & 2.4 min & 0.4 min & 0 min\\
Safe Password Checker & 4096 & 12.0& 0&0 &0 &0 & 20 & 106 KB & 2.3 min & 0.4 min & 0 min\\
One-byte Lookup Table & 4096 & 12.0& 1&1&9.8& 3.6 & 18 & 104 KB & 0.8 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 4096 & 12.0& 1&1&9.6& 8.5 & 18 & 104 KB & 0.7 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 4096 & 12.0&2&2&11.6 &6.7& -& 1.1 MB &4.1 min & 0.8 min & 0.1 min  \\
AES NI mbedTLS 2.15 & 4096 & 12.0&0&0&0 &0&-& 1.1 MB & 2.8 min & 0 min & 0 min  \\
AES OpenSSL 1.1.0  & 4096 & 12.0 & 2&0 &1.4 & 0&-& 1.0 MB  & 3.1 min & 0.2 min & 0 min \\
AES  OpenSSL 1.1.1& 4096 & 12.0 & 2&0 &1.3&0&-& 909 KB & 2.9 min & 0.2 min & 0 min\\
AES  wolfSSL 4.5.0& 4096 & 12.0 &2&0& 0.11& 0 & - &1.1 MB & 3.3 min & 0.1 min & 0 min \\
AES Libgcrypt 1.8.7& 4096 & 12.0 &0 &0 &0&0 &-&4.4 MB & 10.2 min& 0 min & 0 min\\
RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB & 1021.1 min & 45.1 min & 5.5 min\\
RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&-&4.2 MB & 1613.6 min & 51.6 min & 7.9 min\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&-&4.4 MB & 1412.6 min & 23.9 min & 4.3 min\\
Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB & 183.5 min & 24.6 min & 5.2 min\\
GDK 3.24.23 & 4096 & 16.0 & 33&31& 12.1& 6.0&-& 48.5 MB & 60.8 min & 4.1 min & 1.5 min\\
\bottomrule
\end{tabular}
}

@@

\subsection{Result Overview}
Table~\ref{chapter5:table:over_result} presents the overview result. The minimum unit of the program during the experiment is the function. Suppose the function has more than one access map, then the function that is vulnerable to side-channel attacks. We measure the side-channel leakages at two different granularities: the byte level and the cache line level. The result shows that the program has more leaked vulnerabilities and tends to leak more information at the byte level compare with the cache line level. Each time we run the target program under random inputs and record memory accesses.

\subsection{Benchmarks}
\subsubsection{Password Checker}
\begin{figure}
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  for (int i = 0; i < 2; ++i) {
    if (key[i] != pub[i]) {
      return false;
    }
  }
  return true;
}
\end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  bool matched = true;
  for (int i = 0; i < 2; ++i) {
    if (pub[i] != key[i]) 
      matched = false;
  }
  return matched;
}
\end{lstlisting}
  \end{minipage}
  \caption{A password checker. The right version is vulnerable to side-channel attacks. The left version is the fixed version.}\label{fig:chapter5:pwcheck}
\end{figure}

\subsubsection{Lookup Table}
\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
static const uint8_t T[1024] = {
      0x63U, 0x7cU, 0x77U, 0x7bU, 0xf2U, 0x6bU, 0x6fU, 0xc5U,
      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U,
...
output = (T[(key[i]>>24)] << 24) ^
         (T[(key[i+1]>>16) & 0xff] << 16) ^
         (T[(key[i+2]>>8) & 0xff] << 8) ^
         (T[(key[i+3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup Tables with Small Entries.}\label{fig:chapter5:small_lookup}
\end{figure}

\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
static const uint32_t T[256] = {
    0xc66363a5U, 0xf87c7c84U, 0xee777799U, 0xf67b7b8dU,
    0xfff2f20dU, 0xd66b6bbdU, 0xde6f6fb1U, 0x91c5c554U,
    0x60303050U, 0x02010103U, 0xce6767a9U, 0x562b2b7dU,
    0xe7fefe19U, 0xb5d7d762U, 0x4dababe6U, 0xec76769aU};
...
output = (T[(key[i+0]>>24)] << 24) ^
         (T[(key[i+1]>>16) & 0xff] << 16) ^
         (T[(key[i+2]>>8) & 0xff] << 8) ^
         (T[(key[i+3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup Tables with Big Entries.}\label{fig:chapter5:big_lookup}
\end{figure}

\subsection{Case Study: Attacks on Multi-class Classification Inference Engine}
In the section, we demonstrate an attack that can recover the deep learning model inference output by the controlled-channel attack. Running the machine learning inference engine inside the enclave is a typical scenario for machine learning as service. The machine learning service provider upload the the trained model into an enclave running on the cloud platform and provide machine learning service to a third party user. With the help of the enclave, both the model and the user's inferred result is protected from the outside. However, we will show that the above information can be easily retrieved from the untrusted world through the side-channel attack.

We use MNIST as the dataset and LeNet-5 for MNIST digits recognition task. LeNet-5 is known to work well on handwritten digit recognition. We first train the network. The batch size in our experiment is 10 and the numbers of epochs is 30. After the training, the accuracy of the neural networks on test set images is 99.5\%.

Then we use the model to infer the images. During the inference, we also record the page access information.

>>>>

\section{Implementation}
We have implemented a prototype of \ctool{}. It takes an input of ELF binary as well as the source code of the corresponding problem. The front-end of \ctool{} is implemented in Python. It can generate random inputs and test the program with those inputs many times.  The address record part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input. The main component uses \textsf{libelfin}, an open source library to parse ELF binaries and read DWARF debug information. The current implementation can support  64-bits ELF binary in Linux.

@@

\textbf{Benchmark}   & \multicolumn{2}{c}{\textbf{Input Data}} &  \multicolumn{2}{c}{\textbf{\# Leaked Functions}} & \multicolumn{2}{c}{\textbf{Max. Leak (bits)}}   & \multicolumn{2}{c}{\textbf{Program Size}}    & \multicolumn{3}{c}{\textbf{Performance}}    \\ 
\cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7}\cmidrule(lr){8-9}\cmidrule(lr){10-12}& \# & bits &  1 Byte &  64 Bytes & 1 Byte  & 64 Bytes & LoC & Size & Fuzzing & Comparison & Chi-squared
\\\midrule
Unsafe Password Checker& 4096& 12.0& 1&0&0.04&  0& 18 & 104 KB & 2.4 min & 0.4 min & 0 min\\
Safe Password Checker & 4096 & 12.0& 0&0 &0 &0 & 20 & 106 KB & 2.3 min & 0.4 min & 0 min\\
One-byte Lookup Table & 4096 & 12.0& 1&1&7.5& 3.6 & 18 & 104 KB & 0.8 min & 0.1 min & 0 min\\
Four-byte Lookup Table & 4096 & 12.0& 1&1&9.6& 8.5 & 18 & 104 KB & 0.7 min & 0.1 min & 0 min\\
AES T-Table mbedTLS 2.15 & 4096 & 12.0&2&2&11.6 &6.7& -& 1.1 MB &4.1 min & 0.8 min & 0.1 min  \\
AES NI mbedTLS 2.15 & 4096 & 12.0&0&0&0 &0&-& 1.1 MB & 2.8 min & 0 min & 0 min  \\
AES OpenSSL 1.1.0  & 4096 & 12.0 & 1&0 &1.4 & 0&-& 1.0 MB  & 3.1 min & 0.2 min & 0 min \\
AES  OpenSSL 1.1.1& 4096 & 12.0 & 1&0 &1.3&0&-& 909 KB & 2.9 min & 0.2 min & 0 min\\
AES  wolfSSL 4.5.0& 4096 & 12.0 &1&0& 0.11& 0 & - &1.1 MB & 3.3 min & 0.1 min & 0 min \\
AES Libgcrypt 1.8.7& 4096 & 12.0 &0 &0 &0&0 &-&4.4 MB & 10.2 min& 0 min & 0 min\\
RSA mbedTLS 2.15& 4096 & 12.0 &10&8&13.3& 6.0 &-&1.8 MB& 1321.1 min & 63.5 min & 5.1 min \\
RSA OpenSSL 1.1.0& 4096 & 12.0 &14&6&6.7& 4.1 &-& 11 MB & 981.1 min & 75.4 min & 4.5 min\\
RSA OpenSSL 1.1.1& 4096 & 12.0 &6&4&6.3& 2.1&-&13 MB & 1021.1 min & 45.1 min & 5.5 min\\
RSA wolfSSL 4.5.0& 4096 & 12.0 &5&2&3.4& 2.5&-&4.2 MB & 1613.6 min & 51.6 min & 7.9 min\\
RSA Libgcrypt 1.8.7& 4096 & 12.0 &8&6&8.6& 6.6&-&4.4 MB & 1412.6 min & 23.9 min & 4.3 min\\
Tiny DNN & 12000 & - & 17&14&17.1&16.1&-& 4.4 MB & 183.5 min & 24.6 min & 5.2 min\\
GDK 3.24.23 & 4096 & 16.0 & 33&31& 12.1& 6.0&-& 48.5 MB & 60.8 min & 4.1 min & 1.5 min\\
\bottomrule
\end{tabular}
}

@@

Table~\ref{chapter5:table:over_result} presents the overview result. The minimum unit of the program during the experiment is the function. Suppose the function has more than one access map, then the function that is vulnerable to side-channel attacks. We measure the side-channel leakages at two different granularities: the byte level and the cache line level. The result shows that the program has more leaked vulnerabilities and tends to leak more information at the byte level compare with the cache line level. Each time we run the target program under random inputs and record memory accesses. For cryptography programs, we run the target program with $4096$ different inputs. During the fuzzing process, if the program does not have new memory access bitmap after several rounds. We call the fuzzing step is fixed. From the side-channel detection aspect, it is not necessary to continue running the experiments since more rounds do not reveal new leakages. During the experiment, we find AES ciphers reach the fixed point after about 300 rounds and RSA can reach the fixed point after around 500 rounds. Previous work~\cite{217537} also reported similar result. During our experiment, we continue running the experiment until the observe value for the same observation is at least 5 to satisfy the Chi-square test requirement. Therefore, we choose to run all the cipher with different inputs for $4096$ times.  If one program has more than two leaked functions, we run the chi-squared test and calculate the total amount of leakages.

\subsection{Benchmarks}
\subsubsection{Password Checker}
\begin{figure}
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  for (int i = 0; i < 2; ++i) {
    if (key[i] != pub[i]) {
      return false;
    }
  }
  return true;
}
\end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\linewidth}
    \begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none]
bool pwcheck(uint8_t *key, uint8_t *pub) {
  bool matched = true;
  for (int i = 0; i < 2; ++i) {
    if (pub[i] != key[i]) 
      matched = false;
  }
  return matched;
}
\end{lstlisting}
  \end{minipage}
  \caption{A password checker. The left version is vulnerable to side-channel attacks. The right version is the fixed version.}\label{fig:chapter5:pwcheck}
\end{figure}

We illustrate the quantification method on a password checking example.  As shown in Figure~\label{fig:chapter5:pwcheck}, the left version is vulnerable to side-channel attacks because of the early return at line 4. If the first bytes of \textsf{key} and \textsf{pub} are the same, the function will continue running and access the second byte. The right version fixes the vulnerability because the function will continue comparing the second byte even if the first byte is different.  \ctool{} identifies the leakage site in the left figure successfully and estimates the amount of leakage site is $0.04$ bits.

\subsubsection{Lookup Table}
\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
static const uint8_t T[1024] = {
      0x63U, 0x7cU, 0x77U, 0x7bU, 0xf2U, 0x6bU, 0x6fU, 0xc5U,
      0x30U, 0x01U, 0x67U, 0x2bU, 0xfeU, 0xd7U, 0xabU, 0x76U,
...
output = (T[(key[0]>>24)] << 24) ^
         (T[(key[1]>>16) & 0xff] << 16) ^
         (T[(key[2]>>8) & 0xff] << 8) ^
         (T[(key[3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup Tables with Small Entries.}\label{fig:chapter5:small_lookup}
\end{figure}

\begin{figure}
\centering
    \begin{lstlisting}[xleftmargin=.1\textwidth, xrightmargin=.1\textwidth, frame=none]
static const uint32_t T[256] = {
    0xc66363a5U, 0xf87c7c84U, 0xee777799U, 0xf67b7b8dU,
    0xfff2f20dU, 0xd66b6bbdU, 0xde6f6fb1U, 0x91c5c554U,
    0x60303050U, 0x02010103U, 0xce6767a9U, 0x562b2b7dU,
    0xe7fefe19U, 0xb5d7d762U, 0x4dababe6U, 0xec76769aU};
...
output = (T[(key[0]>>24)] << 24) ^
         (T[(key[1]>>16) & 0xff] << 16) ^
         (T[(key[2]>>8) & 0xff] << 8) ^
         (T[(key[3]) & 0xff]);
\end{lstlisting}
  \caption{Lookup Tables with Big Entries.}\label{fig:chapter5:big_lookup}
\end{figure}

We analyze the table lookup with \ctool{}. It is a common operation used by symmetric ciphers like AES. Figure~\ref{fig:chapter5:big_lookup} is from the original AES reference implementation. It uses a lookup table and each entry is 4 bytes, which is vulnerable to side-channel attacks. Most cryptography libraries adopted the mitigated version, shown in Figure~\ref{fig:chapter5:small_lookup}. The evaluation result shows the version with smaller lookup tables leaks less information, which confirm the effectiveness of the mitigation technique.

\subsection{Cryptography Libraries}
For symmetric ciphers, we evaluate \ctool{} on three types implementation of AES. For mebedTLS, we evaluate AES-NI and the reference implementation. We do not find any leakage sites in the AES-NI version. On the other hand, the reference implementation has several leakage sites. The bitsliced version from OpenSSL and wolfSSL should be resistant to side-channel attacks. However, we find they only adopt the protection in the encryption function but leave the key
expansion function unprotected.

\subsection{Machine Learning Applications}
In the section, we demonstrate an attack that can recover the deep learning model inference output by the controlled-channel attack. Running the machine learning inference engine inside the enclave is a typical scenario for machine learning as service. The machine learning service provider upload the the trained model into an enclave running on the cloud platform and provide machine learning service to a third party user. With the help of the enclave, both the model and the user's inferred result is protected from the outside. However, we will show that the above information can be easily retrieved from the untrusted world through the side-channel attack.

We use MNIST as the dataset and LeNet-5 for MNIST digits recognition task. LeNet-5 is known to work well on handwritten digit recognition. We first train the network. The batch size in our experiment is 10 and the numbers of epochs is 30. After the training, the accuracy of the neural networks on test set images is 99.5\%. Then we use the model to infer the images. During the inference, we also record the page access information.
